---
title: "Introduction to R Assignment"
author: "Eliza Stein"
date: "9/4/2020"
output: pdf_document
---

Create 4 vectors:

```{r}

numericYear <- as.numeric(1:10)
factorBird <- as.factor(c('woodpecker', 'owl', 'warbler'))
characterTree <- c('aspen', 'pine', 'oak', 'cottonwood')
boolNest <- c(TRUE, FALSE, FALSE, TRUE)

```

Create data.frame:
```{r}

df1 <- data.frame(a = rpois(10, 2), b = rpois(1000, 2), d = rpois(500, 2), e = rpois(2,2))

```

Write function that finds max and min value of a vector and ignores NAs:
```{r}

#' getMaxMin
#' 
#' @param x a vector
#' @returns a value
#' @examples 
#' getMaxMin(numericYear)

getMaxMin <- function(x){
  max(x, na.rm = TRUE) - min(x, na.rm =TRUE)
  }

```

Write function to find the entries in a vector greater or equal to a threshold:
```{r}

#' getFrac
#' 
#' @param x a vector
#' @param thr a threshold to apply to each vector element
#' @returns a value
#' @examples 
#' getFrac(numericYear, thr = 5)

getFrac <- function(x, thr) {
  length(which(x >= thr)) / length(x)
  }

```

Given list of data.frames, write function that computes column means of each list element and appends them into single output data.frame:

```{r}

#' getlistSummary
#' 
#' @param df a data.frame
#' @returns one data.frame
#' @examples 
#' getlist Summary(df1)

getlistSummary <- function(df) {
  apply(df, 2, mean)
  }

```

Using `mtcars`, write a function that returns avg mpg of cars with $c$ cyliners and $g$ gears that errors out gracefully:

```{r}

data(mtcars)

getMPG <- function(data, c, g) {
  apply(data[1], 2, mean)
}

getMPG(mtcars, mtcars$cyl == 6, mtcars$gear == 4)
```


